Location of Marine fish - general Farms

### 2021-02-09 marine/bivalve/bivalve_farms/STEP2_bivalve_farm_locations.Rmd
finished adding data quality markers to all species groups. Now I need to summarize

For each point, we will add a column for "data quality". It will be scored as very good (1.0), good (0.667), fair (0.333) or poor (0.0).

Very Good qualifications: Locations taken from leases, or from a map with specific locations (i.e. EMOD, ASC, HELCOM etc.).

Good qualifications: Locations are projected or it is a only sample of total locations (NASO maps)

Fair qualifications: A specific number of farms are placed on the coast, without knowing exact locations. Or Per province/state locations (i.e. placing a point randomly in each province) or sub regional location.

Bad qualifications: No data at all (randomly placed point(s) along the coast, a non-specific number), google maps estimates.

>>>>

For each point, we will add a column for "data quality". It will be scored as very good (1.0), good (0.667), fair (0.333) or poor (0.0). 
 - Very Good qualifications: Locations taken from leases, or from a map with specific locations (i.e. EMOD, ASC, HELCOM etc.).
 - Good qualifications: Locations are projected or it is a only sample of total locations (NASO maps). Google maps estimates. 
 - Fair qualifications: A specific number of farms are placed on the coast, without knowing exact locations. Or Per province/state locations (i.e. placing a point randomly in each province) or sub regional location. 
 - Bad qualifications: No data at all (randomly placed point(s) along the coast, a non-specific number).

### 2021-02-09 marine/crustaceans/crustacean_farms/STEP2_crustacean_farm_locations.Rmd
finished adding data quality markers to all species groups. Now I need to summarize

 - Try to obtain exact locations of farms from published source or dataset (such as FAO or a research paper)
 - If there are no exact locations, but the source lists a city or state, place a point in that particular city or state
 -  If there is enough information to know there are a specific number of crustacean farms, equally allocate the farms across the coastline. If there are estimates of farms per state/province, equally allocate them across the state/province, to be even more precise.
 - If there are not exact numbers of farms in the country, but you know there are a lot, randomly place points along the coast line (a non-exact number, like we did for Taiwan bivalve/shrimp). 
 - Lastly, if there is no evidence of marine crustacean farm locations, place a point on the coast of the country (preferably with some intuition/knowledge of where they might be, i.e. what we've done for Russia for bivalves).

@@

farms_idn <- data.frame(lat = c(0.3359943014669836),
                        lon = c(117.55582991782983)) %>%
  mutate(iso3c = "IDN")

@@

farms_chn <- data.frame(lat = c(29.378009267567716),
                        lon = c(121.95043909100868)) %>%
  mutate(iso3c = "CHN")

@@

farms_bgd <- data.frame(lat = c(21.876081791221054, 22.325919306644522),
                        lon = c(89.49499697244659, 91.76441856678511)) %>%
  mutate(iso3c = "BGD")

@@

farms_mmr <- data.frame(lat = c(15.930407995930784, 18.615093163569437),
                        lon = c(94.76647475697742, 94.24290607527016)) %>%
  mutate(iso3c = "MMR")

@@

farms_vnm <- data.frame(lat = c(21.186050529545593, 20.840947248646557, 20.454148639095266, 20.146554460540862, 19.955496263213185, 19.726817666482322, 18.982876968029743, 18.456817613512555, 17.56001328746647, 16.905826522213328, 16.495115996149718, 16.167986126005765, 15.699026568754403, 15.010595152983287, 14.17668770026659, 13.335760529041393, 12.299111935360338, 11.62183927318579, 10.830102342204183, 10.510731358280973, 10.30006571666483, 10.037866832581582, 9.592223563185232, 9.389580381208823, 9.147921315425062, 8.674166818318303, 10.087872204898957, 10.055231),
                        lon = c(107.60858937642442, 106.77685003845498, 106.59728856581118, 106.3298019452741, 106.03097468374126, 105.87661730467457, 105.6165097440173, 105.92726656633255, 106.58039999954293, 107.19194145855845, 107.74891583338649, 108.15075180169012, 108.48016289264334, 108.92174225624275, 109.19617116389627, 109.29183511586322, 109.23699322130719, 109.1546891359726, 108.03702110643216, 106.7310999868549, 106.78122716883196, 106.69637036338817, 106.54126727713718, 106.1857446280396, 105.59613926925006, 105.12379673906345,  104.88743812284027, 105.789267),
                        prod = c(0, 1650, 0, 0, 1005, 970, 0, 200, 110, 20, 82, 0, 135, 0, 130, 0, 0, 5, 0, 250, 0, 637, 1196, 0, 3466, 0, 170, 0), sub_rgn = c("Quang Ninh", "Hai Phong", "Thai Binh", "Nam Dinh", "Ninh Binh", "Thanh Hoa", "Nghe An", "Ha Tinh", "Quang Binh", "Quang Tri", "TT Hue", "Da Nang", "Quang Nam", "Quang Ngai", "Binh Dinh", "Phu Yen", "Khanh Hoa", "Ninh Thuân", "Binh Thuân", "Long An", "Tien Giang", "Ben Tre", "Tra Vinh", "Soc Trang", "Bac Lieu", "Ca Mau", "Kien Giang", "Can Tho")) %>%
  mutate(iso3c = "VNM")

@@

phl_lat_lon <- phl_mudcrab_prod %>%
  left_join(provinces, by = "Province") %>%
  dplyr::select(lat, lon, prod, "sub_rgn" = "Province") %>%
  mutate(iso3c = "PHL")

@@

write.csv(all_farms, here::here("marine/crustaceans/crustacean_farms/data/global_crustacean_farm_lat_lon.csv"), row.names = FALSE)

>>>>

 - Try to obtain exact locations of farms from published source or dataset (such as FAO or a research paper)
 - If there are no exact locations, but the source lists a city or state, place a point in that particular city or state
 -  If there is enough information to know there are a specific number of crustacean farms, equally allocate the farms across the coastline. If there are estimates of farms per state/province, equally allocate them across the state/province, to be even more precise.
 - Lastly, if there is no evidence of marine crustacean farm locations, place a point on the coast of the country (preferably with some intuition/knowledge of where they might be, i.e. what we've done for Russia for bivalves).

For each point, we will add a column for "data quality". It will be scored as very good (1.0), good (0.667), fair (0.333) or poor (0.0). 
 - Very Good qualifications: Locations taken from leases, or from a map with specific locations (i.e. EMOD, ASC, HELCOM etc.).
 - Good qualifications: Locations are projected or it is a only sample of total locations (NASO maps) 
 - Fair qualifications: A specific number of farms are placed on the coast, without knowing exact locations. Or Per province/state locations (i.e. placing a point randomly in each province) or sub regional location. 
 - Bad qualifications: No data at all (randomly placed point(s) along the coast, a non-specific number), google maps estimates.

@@

farms_idn <- data.frame(lat = c(0.3359943014669836),
                        lon = c(117.55582991782983)) %>%
  mutate(iso3c = "IDN") %>%
  mutate(data_quality = 0.0)

@@

farms_chn <- data.frame(lat = c(29.378009267567716),
                        lon = c(121.95043909100868)) %>%
  mutate(iso3c = "CHN") %>%
  mutate(data_quality = 0.0)

@@

farms_bgd <- data.frame(lat = c(21.876081791221054, 22.325670145257305),
                        lon = c(89.49499697244659, 91.76091935028879)) %>%
  mutate(iso3c = "BGD") %>%
  mutate(data_quality = 0.333)

@@

farms_mmr <- data.frame(lat = c(15.930407995930784, 18.615093163569437),
                        lon = c(94.76647475697742, 94.24290607527016)) %>%
  mutate(iso3c = "MMR") %>%
  mutate(data_quality = 0.333)

@@

farms_vnm <- data.frame(lat = c(21.186050529545593, 20.840947248646557, 20.454148639095266, 20.146554460540862, 19.955496263213185, 19.726817666482322, 18.982876968029743, 18.456817613512555, 17.56001328746647, 16.905826522213328, 16.495115996149718, 16.167986126005765, 15.699026568754403, 15.010595152983287, 14.17668770026659, 13.335760529041393, 12.299111935360338, 11.62183927318579, 10.830102342204183, 10.510731358280973, 10.30006571666483, 10.037866832581582, 9.592223563185232, 9.389580381208823, 9.147921315425062, 8.674166818318303, 10.087872204898957, 10.055819944690162),
                        lon = c(107.60858937642442, 106.77685003845498, 106.59728856581118, 106.3298019452741, 106.03097468374126, 105.87661730467457, 105.6165097440173, 105.92726656633255, 106.58039999954293, 107.19194145855845, 107.74891583338649, 108.15075180169012, 108.48016289264334, 108.92174225624275, 109.19617116389627, 109.29183511586322, 109.23699322130719, 109.1546891359726, 108.03702110643216, 106.7310999868549, 106.78122716883196, 106.69637036338817, 106.54126727713718, 106.1857446280396, 105.59613926925006, 105.12379673906345,  104.88743812284027, 105.79073953273914),
                        prod = c(0, 1650, 0, 0, 1005, 970, 0, 200, 110, 20, 82, 0, 135, 0, 130, 0, 0, 5, 0, 250, 0, 637, 1196, 0, 3466, 0, 170, 0), sub_rgn = c("Quang Ninh", "Hai Phong", "Thai Binh", "Nam Dinh", "Ninh Binh", "Thanh Hoa", "Nghe An", "Ha Tinh", "Quang Binh", "Quang Tri", "TT Hue", "Da Nang", "Quang Nam", "Quang Ngai", "Binh Dinh", "Phu Yen", "Khanh Hoa", "Ninh Thuân", "Binh Thuân", "Long An", "Tien Giang", "Ben Tre", "Tra Vinh", "Soc Trang", "Bac Lieu", "Ca Mau", "Kien Giang", "Can Tho")) %>%
  mutate(iso3c = "VNM") %>%
  mutate(data_quality = 0.333)

@@

phl_lat_lon <- phl_mudcrab_prod %>%
  left_join(provinces, by = "Province") %>%
  dplyr::select(lat, lon, prod, "sub_rgn" = "Province") %>%
  mutate(iso3c = "PHL") %>%
  mutate(data_quality = 0.333)

@@

write.csv(all_farms, here::here("marine/crustaceans/crustacean_farms/data/global_crustacean_farm_lat_lon_data_quality.csv"), row.names = FALSE)

all_farms_1 <- all_farms %>%
  dplyr::select(-data_quality)

write.csv(all_farms_1, here::here("marine/crustaceans/crustacean_farms/data/global_crustacean_farm_lat_lon.csv"), row.names = FALSE)
```

### 2021-02-09 marine/marine_fish_general/finfish_farms/STEP2_finfish_farm_locations.Rmd
finished adding data quality markers to all species groups. Now I need to summarize

@@

farms_eu_final <- cbind(farms_eu, eu_countries) %>%
  dplyr::select(-geometry) %>%
  mutate(iso3c = case_when(
    COUNTRY == "Spain" ~ "ESP",
    COUNTRY == "Cyprus" ~ "CYP", 
    COUNTRY == "Norway" ~ "NOR", 
    COUNTRY == "Greece" ~ "GRC",
    COUNTRY == "Malta" ~ "MLT"
  )) %>%
  dplyr::select(-COUNTRY)

@@

farms_ita <- data.frame(do.call(rbind, st_geometry(ita_pts_latlon))) 
names(farms_ita) <- c("lon", "lat")
farms_ita <- farms_ita %>%
  mutate(iso3c="ITA")

@@

farms_fra <- data.frame(do.call(rbind, st_geometry(fra_pts_latlon))) 
names(farms_fra) <- c("lon", "lat")
farms_fra <- farms_fra %>%
  cbind(countries) %>%
  mutate(iso3c = ifelse(country == "France", "FRA", "ISR")) %>%
  dplyr::select(-country, -geometry)

@@

farms_idn <- data.frame(do.call(rbind, st_geometry(idn_pts_latlon))) 
names(farms_idn) <- c("lon", "lat")
farms_idn <- farms_idn %>%
  mutate(iso3c = "IDN")

@@

farms_prt_final <- farms_prt %>%
  mutate(iso3c = "PRT")

@@

farms_irn <- data.frame(lat = c(37.392419247868425),
                        lon = c(50.1602963496454)) %>%
  mutate(iso3c = "IRN")

@@

farms_chn <- data.frame(lat = c(26.649767732301385),
                        lon = c(119.94149300994019)) %>%
  mutate(iso3c = "CHN")

@@

farms_sau <- data.frame(lat = c(20.287253),
                        lon = c(40.030864)) %>%
  mutate(iso3c = "SAU")

@@

farms_mus <- data.frame(lat = c(-20.005039247819017),
                        lon = c(57.67022708374523)) %>%
  mutate(iso3c = "MUS")

@@

farms_are <- data.frame(lat = c(25.604715925918068),
                        lon = c(56.340214330776234)) %>%
  mutate(iso3c = "ARE")

@@

farms_tun_final <- farms_tun %>%
  mutate(iso3c = "TUN")

@@

```{r}
all_points_twn <- rbind(milkfish_points, grouper_points) %>%
  dplyr::mutate(iso3c = "TWN")

@@

```{r}
farms_cri <- data.frame(lat = c(9.423478373794573),
                        lon = c(-84.20910189917947)) %>%
  mutate(iso3c = "CRI")

@@

```{r}
farms_egy <- data.frame(lat = c(31.360400495764903, 31.15023941171644, 31.319036258284083, 31.491306679824632, 31.52619128473819, 31.275726202441984, 29.944394112057978, 27.80632012228518),
                        lon = c(27.236078999801336, 29.81109569981684, 30.225935332660324, 31.4278324391214, 31.849352783373792, 32.30190584291966, 32.54627145839493,  34.29387671355847),
                        rgn_production = c(5, 1521, 20376, 5460, 55551, 16233, 750, 30),
                        subrgn_name = c("Mersa Matruh", "Alexandria", "Behira", "Dakahlia", "Damietta", "Port Said", "Suez", "South Sinai")) %>%
  mutate(iso3c = "EGY")

@@

```{r}
farms_ind <- data.frame(lat = c(9.28696221512509),
                        lon = c(79.13007737814245)) %>%
  mutate(iso3c = "IND")

@@

farms_sgp_final <- farms_sgp %>%
  mutate(iso3c = "SGP")

@@

Now lets map the farms 
```{r}
farms_mys <- data.frame(lat=c(2.131733588116292, 2.8071936098459522, 5.384539285193906, 2.8056383383493353, 2.1305137929032876),
                        lon=c(102.40118069215845, 103.49758024234029, 100.35040003558889, 103.49881667894354, 102.40627304737939)) %>%
  mutate(iso3c = "MYS")

@@

```{r}
farms_bgd <- data.frame(lat=c(21.802433819366538),
                        lon=c(90.40418040967)) %>%
  mutate(iso3c = "BGD")

@@

```{r}
farms_khm <- data.frame(lat=c(10.53427341558665, 10.748668380457524, 10.647924480438327),
                        lon=c(103.57357940185497, 103.6089106992865, 103.5006922685572)) %>%
  mutate(iso3c = "KHM")

@@

farms_kor_final <- farms_kor %>%
  mutate(iso3c = "KOR")

@@

```{r}
farms_hkg <- data.frame(lat_lon = c("22.537974350807968, 114.22465750899093", "22.549021238266082, 114.27266261841545", "22.549243173819686, 114.29054140885648", "22.545901930448537, 114.29912254835972", "22.524524976629923, 114.28385013462695", "22.507936457313377, 114.30641749235996", "22.47796934657302, 114.35412559932351", "22.459641511472412, 114.360272945696", "22.4435502213444, 114.35400029960742", "22.46853714662761, 114.2720207303674", "22.42337637093222, 114.27819733339493", "22.349528341786087, 114.35178911904846", "22.367924650829952, 114.31997002657292", "22.368469602475702, 114.3230438982345", "22.3691151827537, 114.30143307907038", "22.341819373881275, 114.31744391160476", "22.35464650188533, 114.26990023341041", "22.274992746117093, 114.29389242171153", "22.164051938726015, 114.25252757025574", "22.20591578796148, 114.12923505969019", "22.221779736133797, 114.12958553008323", "22.352165476146805, 114.05569941361628", "22.45358281100093, 114.2079128367368", "22.235400816169882, 114.00599898096631", "22.454708931476908, 114.22148845386273", "22.25579039550771, 114.28554310187128")) %>%
  separate(lat_lon, into = c("lat", "lon"), sep = ",") %>%
  mutate(iso3c = "HKG")

@@

write.csv(all_farms, here::here("marine/marine_fish_general/finfish_farms/data/global_finfish_farm_lat_lon.csv"), row.names = FALSE)

>>>>

For each point, we will add a column for "data quality". It will be scored as very good (1.0), good (0.667), fair (0.333) or poor (0.0). 
 - Very Good qualifications: Locations taken from leases, or from a map with specific locations (i.e. EMOD, ASC, HELCOM etc.).
 - Good qualifications: Locations are projected or it is a only sample of total locations (NASO maps). Google maps estimates. 
 - Fair qualifications: A specific number of farms are placed on the coast, without knowing exact locations. Or Per province/state locations (i.e. placing a point randomly in each province) or sub regional location. 
 - Bad qualifications: No data at all (randomly placed point(s) along the coast, a non-specific number).

@@

farms_eu_final <- cbind(farms_eu, eu_countries) %>%
  dplyr::select(-geometry) %>%
  mutate(iso3c = case_when(
    COUNTRY == "Spain" ~ "ESP",
    COUNTRY == "Cyprus" ~ "CYP", 
    COUNTRY == "Norway" ~ "NOR", 
    COUNTRY == "Greece" ~ "GRC",
    COUNTRY == "Malta" ~ "MLT"
  )) %>%
  dplyr::select(-COUNTRY) %>%
  mutate(data_quality = 1.0)

@@

farms_ita <- data.frame(do.call(rbind, st_geometry(ita_pts_latlon))) 
names(farms_ita) <- c("lon", "lat")
farms_ita <- farms_ita %>%
  mutate(iso3c="ITA") %>%
  mutate(data_quality = 0.667)

@@

farms_fra <- data.frame(do.call(rbind, st_geometry(fra_pts_latlon))) 
names(farms_fra) <- c("lon", "lat")
farms_fra <- farms_fra %>%
  cbind(countries) %>%
  mutate(iso3c = ifelse(country == "France", "FRA", "ISR")) %>%
  dplyr::select(-country, -geometry) %>%
  mutate(data_quality = 0.667)

@@

farms_idn <- data.frame(do.call(rbind, st_geometry(idn_pts_latlon))) 
names(farms_idn) <- c("lon", "lat")
farms_idn <- farms_idn %>%
  mutate(iso3c = "IDN") %>%
  mutate(data_quality = 0.667)

@@

farms_prt_final <- farms_prt %>%
  mutate(iso3c = "PRT") %>%
  mutate(data_quality = 0.333)

@@

farms_irn <- data.frame(lat = c(37.392419247868425),
                        lon = c(50.1602963496454)) %>%
  mutate(iso3c = "IRN") %>%
  mutate(data_quality = 0.0)

@@

farms_chn <- data.frame(lat = c(26.649767732301385),
                        lon = c(119.94149300994019)) %>%
  mutate(iso3c = "CHN") %>%
  mutate(data_quality = 0.0)

@@

farms_sau <- data.frame(lat = c(20.27293672234808),
                        lon = c(40.03614937279944)) %>%
  mutate(iso3c = "SAU") %>%
  mutate(data_quality = 0.667)

@@

farms_mus <- data.frame(lat = c(-20.005039247819017),
                        lon = c(57.67022708374523)) %>%
  mutate(iso3c = "MUS") %>%
  mutate(data_quality = 0.0)

@@

farms_are <- data.frame(lat = c(25.604715925918068),
                        lon = c(56.340214330776234)) %>%
  mutate(iso3c = "ARE") %>%
  mutate(data_quality = 0.333)

@@

farms_tun_final <- farms_tun %>%
  mutate(iso3c = "TUN") %>%
  mutate(data_quality = 0.333)

@@

```{r}
all_points_twn <- rbind(milkfish_points, grouper_points) %>%
  dplyr::mutate(iso3c = "TWN") %>%
  mutate(data_quality = 0.333)

@@

```{r}
farms_cri <- data.frame(lat = c(9.423478373794573),
                        lon = c(-84.20910189917947)) %>%
  mutate(iso3c = "CRI") %>%
  mutate(data_quality = 0.667)

@@

```{r}
farms_egy <- data.frame(lat = c(31.360400495764903, 31.15023941171644, 31.319036258284083, 31.491306679824632, 31.52619128473819, 31.275726202441984, 29.944394112057978, 27.80632012228518),
                        lon = c(27.236078999801336, 29.81109569981684, 30.225935332660324, 31.4278324391214, 31.849352783373792, 32.30190584291966, 32.54627145839493,  34.29387671355847),
                        rgn_production = c(5, 1521, 20376, 5460, 55551, 16233, 750, 30),
                        subrgn_name = c("Mersa Matruh", "Alexandria", "Behira", "Dakahlia", "Damietta", "Port Said", "Suez", "South Sinai")) %>%
  mutate(iso3c = "EGY") %>%
  mutate(data_quality = 1.0)

@@

```{r}
farms_ind <- data.frame(lat = c(9.28696221512509),
                        lon = c(79.13007737814245)) %>%
  mutate(iso3c = "IND") %>%
  mutate(data_quality = 0.667)

@@

farms_sgp_final <- farms_sgp %>%
  mutate(iso3c = "SGP") %>%
  mutate(data_quality = 0.333)

@@

Now lets map the farms 
```{r}
farms_mys <- data.frame(lat=c(2.131733588116292, 2.8071936098459522, 5.384539285193906, 2.8056383383493353, 2.1305137929032876),
                        lon=c(102.40118069215845, 103.49758024234029, 100.35040003558889, 103.49881667894354, 102.40627304737939)) %>%
  mutate(iso3c = "MYS") %>%
  mutate(data_quality = 0.333)

@@

```{r}
farms_bgd <- data.frame(lat=c(21.802433819366538),
                        lon=c(90.40418040967)) %>%
  mutate(iso3c = "BGD") %>%
  mutate(data_quality = 0.0)

@@

```{r}
farms_khm <- data.frame(lat=c(10.53427341558665, 10.748668380457524, 10.647924480438327),
                        lon=c(103.57357940185497, 103.6089106992865, 103.5006922685572)) %>%
  mutate(iso3c = "KHM") %>%
  mutate(data_quality = 0.333)

@@

farms_kor_final <- farms_kor %>%
  mutate(iso3c = "KOR") %>%
  mutate(data_quality = 0.333)

@@

```{r}
farms_hkg <- data.frame(lat_lon = c("22.537974350807968, 114.22465750899093", "22.549021238266082, 114.27266261841545", "22.549243173819686, 114.29054140885648", "22.545901930448537, 114.29912254835972", "22.524524976629923, 114.28385013462695", "22.507936457313377, 114.30641749235996", "22.47796934657302, 114.35412559932351", "22.459641511472412, 114.360272945696", "22.4435502213444, 114.35400029960742", "22.46853714662761, 114.2720207303674", "22.42337637093222, 114.27819733339493", "22.349528341786087, 114.35178911904846", "22.367924650829952, 114.31997002657292", "22.368469602475702, 114.3230438982345", "22.3691151827537, 114.30143307907038", "22.341819373881275, 114.31744391160476", "22.35464650188533, 114.26990023341041", "22.274992746117093, 114.29389242171153", "22.164051938726015, 114.25252757025574", "22.20591578796148, 114.12923505969019", "22.221779736133797, 114.12958553008323", "22.352165476146805, 114.05569941361628", "22.45358281100093, 114.2079128367368", "22.235400816169882, 114.00599898096631", "22.454708931476908, 114.22148845386273", "22.25579039550771, 114.28554310187128")) %>%
  separate(lat_lon, into = c("lat", "lon"), sep = ",") %>%
  mutate(iso3c = "HKG") %>%
  mutate(data_quality = 1.0)

@@

all_farms_1 <- all_farms %>%
  dplyr::select(-data_quality)

write.csv(all_farms_1, here::here("marine/marine_fish_general/finfish_farms/data/global_finfish_farm_lat_lon.csv"), row.names = FALSE)

write.csv(all_farms, here::here("marine/marine_fish_general/finfish_farms/data/global_finfish_farm_lat_lon_data_quality.csv"), row.names = FALSE)
